---
title: "DATA EXTRACTION & QA-QC FOR PROF DR AK SAHOO"
author: "Ankit Anand"
date: "2026-01-05"
output: html_document
---

This R Markdown file is designed to prepare, clean, and quality-check a multi-country panel dataset for empirical economic analysis, particularly for foreign aid, development indicators, and DEA/econometric applications.

-\> The entire workflow follows three broad objectives:

1.) Create a consistent panel dataset (Country × Year × Indicators)

2.) Identify missing, weak, or unreliable data

3.) Help decide which countries, indicators, and years form a balanced dataset.

No advanced R knowledge is required to understand the logic — each step reflects a data question rather than a programming task.

```{r}

```

🧱 Step-by-Step Logic of the File
1. Loading Required Tools

The file first loads a few standard R libraries.
These libraries allow us to:

A)Read Excel files
B)Reshape data from wide to long format
C) Summarise missing values
D) Create tables and charts
E) Export clean datasets back to Excel

This ensures the analysis is reproducible and transparent.
```{r, echo = FALSE,message=FALSE, warning=FALSE}
############################################
# 1. Load Required Libraries
############################################

library(readxl)
library(dplyr)
library(tidyr)
library(ggplot2)
library(writexl)

```


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
